The title

### 2023-04-14 doc/multiverse.Rmd
Rerun pipeline
Add ethnicity to models
Closes #54

```{r PA-by-sleep-regularity-fig-by-pa-mostactivehr, fig.cap = "Physical activity by sleep regularity moderated by most active hour"}
knitr::include_graphics(here::here(purdy_pictures_by_pa_mostactivehr$predictor_sleep_regularity_lag), error = FALSE)
```

>>>>

```{r PA-by-sleep-regularity-fig-by-pa-mostactivehr, fig.cap = "Physical activity by sleep regularity moderated by most active hour"}
knitr::include_graphics(here::here(purdy_pictures_by_pa_mostactivehr$predictor_sleep_regularity_lag), error = FALSE)
```
\clearpage

## ethnicity

```{r}
tar_load(model_tables_by_ethnicity)
tar_load(purdy_pictures_by_ethnicity)
```

### The effects of physical activity volume on sleep by ethnicity

We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
We estimated the effect of physical activity volume on sleep by ethnicity, and the results are presented in Table \@ref(tab:sleep-outcomes-by-ethnicity) and Figure \@ref(fig:sleep-by-volume-fig-by-ethnicity)

```{r sleep-outcomes-by-ethnicity}
papaja::apa_table(
  model_tables_by_ethnicity$sleep$data,
  caption = model_tables_by_ethnicity$sleep$caption,
  note = model_tables_by_ethnicity$sleep$note,
  col_spanners = model_tables_by_ethnicity$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r sleep-by-volume-fig-by-ethnicity, fig.cap = "Sleep metrics on Physical activity volume by ethnicity"}
knitr::include_graphics(here::here(purdy_pictures_by_ethnicity$predictor_pa_volume), error = FALSE)
```

### The effects of physical activity intensity on sleep by ethnicity

We estimated how physical activity intensity affects sleep across ethnicity.
We present the results in Table \@ref(tab:sleep-outcomes-by-ethnicity) and Figure \@ref(fig:sleep-by-intensity-fig-by-ethnicity).

```{r sleep-by-intensity-fig-by-ethnicity, fig.cap = "Sleep metrics on Physical activity intensity moderated by ethnicity"}
knitr::include_graphics(here::here(purdy_pictures_by_ethnicity$predictor_pa_intensity), error = FALSE)
```

We estimated the effect of sleep duration on physical activity by ethnicity.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-ethnicity) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-ethnicity).

```{r pa-outcomes-by-ethnicity}
papaja::apa_table(
  model_tables_by_ethnicity$physical_activity$data,
  caption = model_tables_by_ethnicity$physical_activity$caption,
  note = model_tables_by_ethnicity$physical_activity$note,
  col_spanners = model_tables_by_ethnicity$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r PA-by-sleep-duration-fig-by-ethnicity, fig.cap = "Physical activity by sleep duration moderated by ethnicity"}
knitr::include_graphics(here::here(purdy_pictures_by_ethnicity$predictor_sleep_duration_lag), error = FALSE)
```

We estimated the effect of sleep efficiency on physical activity by ethnicity.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-ethnicity) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-ethnicity).

```{r PA-by-sleep-efficiency-fig-by-ethnicity, fig.cap = "Physical activity by sleep efficiency moderated by ethnicity"}
knitr::include_graphics(here::here(purdy_pictures_by_ethnicity$predictor_sleep_efficiency_lag), error = FALSE)
```

We estimated the effect of sleep onset on physical activity by ethnicity.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-ethnicity) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-ethnicity).

```{r PA-by-sleep-onset-fig-by-ethnicity, fig.cap = "Physical activity by sleep onset moderated by ethnicity"}
knitr::include_graphics(here::here(purdy_pictures_by_ethnicity$predictor_sleep_onset_lag), error = FALSE)
```

We estimated the effect of sleep regularity on physical activity by ethnicity.
Results are presented in Table \@ref(tab:pa-outcomes-by-ethnicity) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-ethnicity).

```{r PA-by-sleep-regularity-fig-by-ethnicity, fig.cap = "Physical activity by sleep regularity moderated by ethnicity"}
knitr::include_graphics(here::here(purdy_pictures_by_ethnicity$predictor_sleep_regularity_lag), error = FALSE)
```
